---
title: Stat 3155 Homework 5, Logistic Regression
author: Thomas Maltese
date: "April 24th, 2018"
output: pdf_document
---

# Problem 1

Part A.
```{r}
b = c(0.11, 0.16, -0.57, -0.66, 0.47, -1.67)

x = c(0, 1, 0, 0, 1)
logit = b[1] + sum(b[2:length(b)] * x)
p = exp(logit) / (1 + exp(logit))
cat(p, '\n')

x = c(1, 0, 1, 1, 0)
logit = b[1] + sum(b[2:length(b)] * x)
p = exp(logit) / (1 + exp(logit))
cat(p, '\n')
```

Therefore, the probability that a male, protestant,
and republican supports laws legalizing abortion
is approximately 10.62%, and the probability that a femaile,
catholic, and democrat supports laws legalizing abortion
is approximately 51.99%

Part B.

$b_1$ = 0.16 means that if the subject is Female, the
odds of the subject supporting laws legalizing abortion
change by a multiplicative factor of about:
```{r}
cat(exp(0.16), '\n')
```
which is an increase of about 17.35% percent,
when compared with male subjects, ceteris paribus.

and $b_2$ = -0.57 means that if the subject is Protestant, the
odds of the subject supporting laws legalizing abortion
change by a multiplicative factor of about
```{r}
cat(exp(-0.57), '\n')
```
which is a decrease of about 43.44% when compared with
non-protestant subject, ceteris paribus.

Part C.

let SE($b_1$) = 0.0064
The confidence interval is computed with:
```{r}
b1 = 0.16
s = 0.0064
z = abs(qnorm(0.05 / 2))
upper = b1 + z * s
lower = b1 - z * s
cat(lower, upper, '\n')
```
then:
we say that we are 95% confident that when the subject is Female, ceteris
paribus, the odds that the subject suppors laws legalizing abortion
are increased by a multiplicative factor between $e^{0.1474} \approx 15.88$ percent and
$e^{0.1725} \approx 18.82$ percent

Part D.
```{r}
b1 = 0.16
s = 0.0064
z = b1 / s
zz = abs(qnorm(0.05 / 2))
if (z > zz) {
	cat("We reject the null hypothesis\n");
} else {
	cat("We fail to reject the null hypothesis\n");
}
```

Part E.

Let SE($b_2$) = 0.38
The confidence interval is computed with:
```{r}
b2 = -0.57
s = 0.38
z = abs(qnorm(0.05 / 2))
upper = b2 + z * s
lower = b2 - z * s
cat(lower, upper, '\n')
```
we say that we are 95% confident that when the subject is is Protestant,
ceteris paribus, the odds that the subject supports laws legalizing abortion
are increased by a multiplicative factor between $e^{-1.3147} \approx 17.47$ percent and
$e^{0.1747} \approx 119.09$ percent; these multiplicative factors correspond with
an approximate 82.53% decrease and 19.09% increase, respectively.

Since we get conflicting answers (being Protestant could mean an increase or decrease)
in the probability!) we conclude that it doesn't have much predictive power.


# Problem 2

```{r}
data =read.table("data.txt", sep=" ", header=T)
print(data)
attach(data)
model = glm(cbind(Yes, No) ~ factor(Gender) + factor(Race), family=binomial)
summary(model)
```

Part A.

The estimates for $\beta_1$ and $\beta_2$ are 0.7159 and -1.3859 respectively.

Part B.

The probability of observing a response 'Yes' from a black female is 
```{r}
logit = predict(model, newdata=data.frame(Gender="female", Race="black"))
cat(exp(logit) / (1 + exp(logit)), '\n')
```
Which is approximately 38%

The probability observing a response 'Yes' from a white male is 
```{r}
logit = predict(model, newdata=data.frame(Gender="male", Race="white"))
cat(exp(logit) / (1 + exp(logit)), '\n')
```
Which is approximately 23.89%

Part C.

```{r}
b1  = 0.7159
sb1 = 0.2246
z = abs(qnorm(0.05 / 2))
upper = b1 + z * sb1
lower = b1 - z * sb1
cat(lower, upper, '\n')
```
We are 95% confident that, when the subject is male, ceteris paribus,
the odds of the subject having had intercourse increases by a multiplicative
factor somewhere between $e^{0.2756}$ and $e^{1.1561}$, which
corresponds with an increase of around 131.73% and an increase
of around 317.75%, respectively.

Part D.

```{r}
b1  = 0.7159
sb1 = 0.2246
z = b1 / sb1  # could also get from glm() output...
zz = abs(qnorm(0.05 / 2))
if (z > zz) {
	cat("We reject the null hypothesis\n");
} else {
	cat("We fail to reject the null hypothesis\n");
}
```
